Secure Composition \\ of Robust and Optimising Compilers

### 2024-05-16 csf2/main.tex
add text

@@

>>>>

\subsection{$\Lspec$: A Memory-Unsafe Language with Speculation}\label{subsec:lspec}

$\Lspec$ extends $\Lscct$ (\Cref{subsec:lscct}) with speculative dynamic semantics. 
After branching or accessing memory, speculation can start and run subsequent code in a predetermined window until a rollback of operational state is performed. 
Within such windows, data is leaked, marked as high $\ird{\lock}$ and with an annotation that indicates the respective speculative execution variant.
In terms of language features, $\Lspec$ supports a barrier operation $\ird{\lbarrier}$ that blocks speculative execution. 
The trace model is extended with $\ird{\ev{Spec}}$, $\ird{\ev{Rlb}}$, and $\ird{\ev{Barrier}}$ events that signal the respective operational action. 
A barrier prevents any events whatsoever besides $\ird{\ev{Rlb}}$ when run in speculative execution mode and does nothing when run in normal mode.

@@

\subsection{Robust Speculative Safety Preservation}\label{subsec:cs:ss}

\vspace{-1em}
\begin{center}\small
  \begin{align*}
    \ccspec(\obj{\lifz{\expr[_0]}{\expr[_1]}{\expr[_2]}}) & = \lifz[\ird]{\ccspec{\left(\obj{\expr[_0]}\right)}}{\\&\ird{\lbarrier;}\ccspec{\left(\obj{\expr[_1]}\right)}\\&}{\ird{\lbarrier;}\ccspec{\left(\ird{\expr[_2]}\right)}} \\
  \end{align*}
\end{center}
% \vspace{-2em}
%
\begin{theorem}[$\ccspec$ is secure with respect to \gls*{ss}]\label{thm:ccspec:rtp:spec}
  $\rtp{\ccspec}{\specmssafe}$ % \Coqed
\end{theorem}
